A boundary integral equation approach to computing eigenvalues of the Stokes operator

### 2019-04-11 doc/draft-01-stokes/02prelim.tex
cleaning up paper and adding annulus discretization plot

For a given velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor, i.e.
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.
If $\Gamma$ is the boundary of a region $\Omega$ and $\bnu$ is the outward
normal to $\Gamma$, the surface traction $\bt$ on $\Gamma$ 
is the Neumann data, i.e. 
\begin{equation}
\bt = \bsigma \cdot \bnu \, .
\end{equation}

@@

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, d \by = f(\xx) \; .
  \nonumber
\end{equation}
We consider here
free-space Green's functions, i.e. fundamental solutions which satisfy
radiation conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation,
\begin{equation}
  \Delta ( \Delta + k^2 ) u = 0 \; , \label{eq:obiharm} \nonumber
\end{equation}
is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
  \label{eq:Gbh}
\end{equation}
where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

@@

Recall that, in the case that $k=i\alpha$ for some real-valued $\alpha$,
the oscillatory Stokes equations \cref{eq:ostokes}
are known as the modified Stokes equations and are of particular
interest for their application to the analysis and numerical
simulation of unsteady flow
\cite{Pozrikidis1992,biros2002embedded,
  jiang2013second,ladyzhenskaya1969mathematical}.
The equations are well-studied in that setting and
integral representations which lead to second kind
integral equations have been developed. We review
some of the relevant results here, translating to
the oscillatory setting.

@@

\begin{proof}
  Suppose that $\xx \in \Omega$.
  By the definitions of $\GG$ and $\Glap$, we have
  \begin{equation*}
    \bu(\xx) = \int_\Omega -(\Delta_x + k^2) \GG(\xx,\yy) \bu(\yy)
    + \nabla \otimes \nabla \Glap(\xx,\yy) \bu(\yy) \, dV(\yy) \; .
  \end{equation*}
  Applying Green's identity and the divergence theorem, we
  obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG(\xx,\yy) \partial_\nu \bu
    - \partial_\nu \GG(\xx,\yy) \bu
    - \nabla \Glap(\xx,\yy) (\bnu \cdot \bu) \, dS 
    - \int_\Omega \GG(\xx,\yy) (\Delta + k^2) u \, dV \; .
    \nonumber
  \end{equation}
  Substituting the definition of the PDE and applying the divergence
  theorem again, we obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG \partial_\nu \bu - p \GG \bnu - \partial_\nu \GG \bu
    - \nabla \Glap (\bnu \cdot \bu) \, dS  \; . \label{eq:rep_proof_1}
  \end{equation}
  From the divergence theorem and the divergence-free properties of
  $\uu$ and $\GG$, we then get

@@

Without modification, the standard layer potentials
can result in rank-deficient representations for
the boundary value problems. The nature of this deficiency
is treated below but for now we introduce a standard
operator used to correct this. For any integrable density
$\bmu$, let $\cW[\bmu]$ be defined by

>>>>

For a velocity field $\bu$ and pressure $p$, let $\bsigma(\bu,p)$
denote the Cauchy stress tensor is given by
\begin{equation}
\bsigma(\uu,p) = -p \II + 2 \be(\bu) \, ,
\end{equation}
where $\be(\bu)$ is the strain tensor given by
\begin{equation}
e_{ij}(\bu) = \frac{1}{2} \left( \partial_{x_j} u_i + \partial_{x_i} u_j \right) \; .
\end{equation}
When it is clear from context, we will drop the dependence of
$\bsigma$ on $\bu$ and $p$.
If $\Gamma$ is the boundary of a region $\Omega$ and $\bnu$ is the outward
normal to $\Gamma$, the surface traction $\bt$ on $\Gamma$ 
is the Neumann data, i.e. 
\begin{equation}
\bt = \bsigma \cdot \bnu \, .
\end{equation}

@@

Let $\mathcal{L}_x$ denote a linear differential operator. A fundamental
solution $G(\xx,\yy)$ of $\mathcal{L}_x$ satisfies the equation
$\mathcal{L}_x G(\xx,\yy) = \delta_y(\xx)$ in the distributional sense, i.e.
for sufficiently smooth $f$
\begin{equation}
  \mathcal{L}_x \int_{\R^2} G(\xx,\yy) f(\yy) \, d \by = f(\xx) \; .
  \nonumber
\end{equation}
We consider here
free-space Green's functions, i.e. fundamental solutions which satisfy appropriate
radiation conditions as $|\xx-\yy| \to \infty$.
The Green's function of the oscillatory biharmonic equation,
\begin{equation}
  \Delta ( \Delta + k^2 ) u = 0 \; , \label{eq:obiharm} \nonumber
\end{equation}
is given by 
\begin{equation}
  \Gbh(\xx,\yy) = \frac{1}{k^2}
  \left (\frac{1}{2\pi} \log |\xx-\yy| +
  \frac{i}{4} H_0^{(1)}(k|\xx-\yy|) \right ) \, ,
  \label{eq:Gbh}
\end{equation}
where $k$ is the Helmholtz parameter in the oscillatory biharmonic equation,
and $H_{0}^{1}(r)$ is the Hankel function of the first kind of order zero.
Note that this is a scaled difference of the Green's function for
Laplace, i.e.

@@

Recall that, in the case $k=i\alpha$ for some real-valued $\alpha$,
the oscillatory Stokes equations \cref{eq:ostokes}
are known as the modified Stokes equations and are of particular
interest for their application to the analysis and numerical
simulation of unsteady flow
\cite{Pozrikidis1992,biros2002embedded,
  jiang2013second,ladyzhenskaya1969mathematical}.
The equations are well-studied in that setting and
integral representations which lead to second kind
integral equations have been developed. We review
some of the relevant results here, translating to
the oscillatory setting.

@@

\begin{proof}
  Suppose that $\xx \in \Omega$.
  By the definitions of $\GG$ and $\Glap$, we have
  \begin{equation*}
    \bu(\xx) = \int_\Omega -(\Delta + k^2) \GG(\xx,\yy) \bu(\yy)
    + \nabla \otimes \nabla \Glap(\xx,\yy) \bu(\yy) \, dV(\yy) \; .
  \end{equation*}
  Applying Green's identity and the divergence theorem, we
  obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG(\xx,\yy) \partial_\nu \bu
    - \partial_\nu \GG(\xx,\yy) \bu
    - \nabla \Glap(\xx,\yy) (\bnu \cdot \bu) \, dS 
    - \int_\Omega \GG(\xx,\yy) (\Delta + k^2) u \, dV \; .
    \nonumber
  \end{equation}
  Substituting the definition of the PDE and applying the divergence
  theorem again, we obtain
  \begin{equation}
    \bu(\xx) = \int_\Gamma \GG \partial_\nu \bu - p \GG \bnu - \partial_\nu \GG \bu
    - \nabla \Glap (\bnu \cdot \bu) \, dS  \; . \label{eq:rep_proof_1}
  \end{equation}
  From the divergence theorem and the divergence-free properties of
  $\uu$ and $\GG$, we then get

@@

Without modification, the standard layer potentials
can result in rank-deficient representations for
the boundary value problems. The nature of this deficiency
is treated in~\cref{sec:analysis} but for now we introduce a standard
operator used to correct this. For any integrable density
$\bmu$, let $\cW[\bmu]$ be defined by
